The Role of Variability in Learning Generalization: A Computational Modeling Approach

### 2024-05-26 Presentation/slides.qmd
some slide tweaks

---
title: "The Role of Variability in Learning Generalization: A Computational Modeling Approach"
subtitle: "Dissertation Defense"
page-layout: full
aliases:
  - /slides.html
format: 
  html: default
    #toc: true
    #shift-heading-level-by: 1
    #toc-expand: true
  clean-revealjs:
    #theme: moon #white
    #output-ext: revealjs.html
    output-file: slides_revealjs
    slideNumber: true
    hash-type: number # Use slide numbers in the URL hash
    center: true
    scrollable: true
    chalkboard:
      theme: whiteboard
  # pptx:
  #   incremental: false
  # hugo-md:
  #   include: false
  #   html-math-method: mathjax
  #   output-file: slides_hugo.md
  # gfm:
  #   output: false
  #   output-file: slides_gfm.md
author:
  - name: Thomas Gorman
    url: https://tegorman13.github.io
    orcid: 0000-0001-5366-5442
    affiliations:
      - name: Indiana University
        department: Psychological & Brain Sciences, Cognitive Science
params:
  start_slide: 0
#engine: knitr
---

@@

::: {.content-visible when-format="html"}
![](assets/htt_vid.mov){height="540" loop="true" autoplay="true"}
:::

@@

::: {.content-visible when-format="html"}
![](assets/htw_vid.mov){height="540" loop="true" autoplay="true"}
:::

>>>>

---
title: "The Role of Variability in Learning Generalization: A Computational Modeling Approach"
page-layout: full
aliases:
  - /slides.html
css: /Assets/Style/slides.css
format: 
  html: 
    subtitle: "Dissertation Defense"
    #toc: true
    #shift-heading-level-by: 1
    #toc-expand: true
  clean-revealjs:
    #theme: moon #white
    #output-ext: revealjs.html
    # template-partials:
    #   - assets/title-slide.html
    output-file: slides_revealjs
    date: 05/28/204
    slideNumber: true
    hash-type: number # Use slide numbers in the URL hash
    center: true
    scrollable: true
    chalkboard:
      theme: whiteboard
  # pptx:
  #   incremental: false
  # hugo-md:
  #   include: false
  #   html-math-method: mathjax
  #   output-file: slides_hugo.md
  # gfm:
  #   output: false
  #   output-file: slides_gfm.md
author:
  - name: Thomas Gorman
    url: https://tegorman13.github.io
    orcid: 0000-0001-5366-5442
    affiliations:
      - name: Indiana University
        department: Psychological & Brain Sciences, Cognitive Science
params:
  start_slide: 0
#engine: knitr
---

@@

::: {.content-visible when-format="html"}
![](assets/htt_vid.mov){height="540" loop="true" autoplay="true" style="max-width: 100%"}
:::

@@

::: {.content-visible when-format="html"}
![](assets/htw_vid.mov){height="400" loop="true" autoplay="true"}
:::
-   A total of 156 participants from IU's online subject pool
-   Varied group trains from 3 "velocity bands", constant group from 1
